\documentclass[a4paper,11pt]{article}

% Packages
\usepackage[english]{babel}
\usepackage{latexsym}
\usepackage{marvosym}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{color}
\usepackage{hyperref}
\usepackage{verbatim}
\input{glyphtounicode}

% Page styling
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

% URL styling
\urlstyle{same}

% Set link color
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue
}

% Text alignment
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
}{}
{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumePosition}[4]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \small #4 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProject}[3]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \small#2 & \small\href{#1}{\underline{#3}} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%--------------------HEADING--------------------
\begin{center}
    \textbf{\Huge \scshape Areeb Ahmed Shariff} \\ \vspace{1pt}
    \small (+91) 95913-07017 $|$ \href{mailto:areebshariff@acm.org}{\underline{areebshariff@acm.org}} $|$
    \href{https://linkedin.com/in/areebahmeddd}{\underline{linkedin.com/areebahmeddd}} $|$
    \href{https://github.com/areebahmeddd}{\underline{github.com/areebahmeddd}}
\end{center}

%--------------------EDUCATION--------------------
\section{Education}
\resumeSubHeadingListStart
    \resumePosition
        {Dayananda Sagar College of Engineering}{Bengaluru, India}
        {Bachelor of Engineering -- Computer Science and Business Systems}{2022 -- 2026}
\resumeSubHeadingListEnd

%--------------------TECHNICAL SKILLS--------------------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=-2pt]
    \small{
        \item{\textbf{Languages}{: Python, Go, Bash}}
        \item{\textbf{Frameworks}{: Django, FastAPI, Pytest, Pydantic, SQLAlchemy, SocketIO, Crawl4AI, Streamlit, Gin}}
        \item{\textbf{Developer Tools}{: Docker, Kubernetes, OpenTofu, GitHub Actions, AWS, GCP, Monitoring, GitOps}}
    }
\end{itemize}

%--------------------EXPERIENCE--------------------
\section{Experience}
\resumeSubHeadingListStart
    \resumePosition
        {DevOps Engineer}{October 2024 -- Present}
        {Open Healthcare Network}{Kochi, India}
    \resumeItemListStart
        \resumeItem{Migrated Kubernetes-based deployment from Google Cloud to Amazon EC2 with \textbf{Docker Swarm}, optimizing infrastructure costs by \textbf{60\%}.}
        \resumeItem{Automated frontend deployment using \textbf{Terraform}, serving static files via \textbf{Google Cloud Storage} with CDN, ALB, and SSL-enabled security.}
        \resumeItem{Developed \textbf{Bash scripts} to automate backend deployment on \textbf{Azure Container Apps}, integrating PostgreSQL Flexible Server, Redis Cache, and S3-compatible storage via \textbf{Flexify.IO}.}
    \resumeItemListEnd

    \resumePosition
        {Backend Engineer}{October 2025 -- December 2025}
        {NeoSapien}{Bengaluru, India}
    \resumeItemListStart
        \resumeItem{Improved \textbf{Gemini + PyAnnote} speech-to-text pipeline by reducing CER and DER via context engineering, using custom evals against labeled audio benchmarks.}
        \resumeItem{Migrated \textbf{10+ Express.js} endpoints to \textbf{FastAPI} and updated unit and integration tests in \textbf{Pytest} to align with CI pipeline requirements.}
        \resumeItem{Prototyped \textbf{Chrome extension} in \textbf{React} within \textbf{24 hours} to validate extending Neo 1 features to online meetings, enabling live audio capture and streaming to backend services.}
    \resumeItemListEnd

    \resumePosition
        {Software Consultant}{February 2025 -- April 2025}
        {Embeddings Corporation}{Remote}
    \resumeItemListStart
        \resumeItem{Built RAG-based AI agent with \textbf{Pydantic AI} that streamed responses in real time, crawled sitemaps asynchronously with \textbf{Crawl4AI}, and chunked content by smart boundaries (code blocks, paragraphs).}
        \resumeItem{Created API-based knowledge management system with \textbf{Gemini 2.5 Pro} for analysis, \textbf{Ollama's nomic-embed-text} for embeddings, and \textbf{Supabase} for vector storage and fast semantic search.}
        \resumeItem{Updated \textbf{infrastructure documentation} with self-hosting and deployment guides for AWS.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%--------------------PROJECTS--------------------
\section{Projects}
\resumeSubHeadingListStart
    \resumeProject
        {https://github.com/areebahmeddd/superbox.ai}{\textbf{superbox.ai} $|$ \emph{Go, Python, React, AWS Lambda, WebSocket API, S3, Fargate}}{GitHub}
        \resumeItemListStart
            \resumeItem{Developed \textbf{marketplace for MCP servers} with 5-step automated security pipeline (SonarCloud, Trivy, Bandit, Snyk, GitGuardian) and S3-backed registry for centralized discovery and deployment.}
            \resumeItem{Engineered hybrid backend with \textbf{Golang REST API} for server management and \textbf{Python CLI} for authentication, security scanning, and tool discovery.}
            \resumeItem{Designed AWS Lambda–based \textbf{sandboxed execution environment} using WebSocket API Gateway for persistent MCP connections, enabling isolated server execution and real-time JSON-RPC communication.}
        \resumeItemListEnd
    \resumeProject
        {https://github.com/areebahmeddd/cognito.ai}{\textbf{cognito.ai} $|$ \emph{FastAPI, Next.js, Elasticsearch, Vertex AI, MongoDB, Google Compute Engine}}{GitHub}
        \resumeItemListStart
            \resumeItem{Developed natural-language \textbf{forensic evidence discovery engine} that enables investigators to query massive UFDR device exports using conversational AI instead of manual data searching.}
            \resumeItem{Built FastAPI backend with \textbf{Elasticsearch indexing pipeline} to ingest and normalize UFDR data, enabling \textbf{Gemini-based intent analysis} for natural language search over forensic datasets.}
            \resumeItem{Created \textbf{Next.js dashboard} with TypeScript for case management, PDF report generation for forensic documentation, and NextAuth-based session management using \textbf{MongoDB}.}
        \resumeItemListEnd
    \resumeProject
        {https://github.com/SpaceTesla/Mivro}{\textbf{Mivro} $|$ \emph{Django, OpenFoodFacts API, Manifest V3, Flutter, Firebase, AWS Lightsail}}{GitHub}
        \resumeItemListStart
            \resumeItem{Developed cross-platform app and web extension for \textbf{personalized product profiling} in food, drink, cosmetic, medicine, and pet food categories.}
            \resumeItem{Integrated \textbf{Claude API} to \textbf{categorize nutrients} based on user-specific health data, \textbf{analyse health risks} associated, and \textbf{recommend healthier food options} or lifestyle changes.}
            \resumeItem{Implemented custom searching algorithm using \textbf{fuzzy matching} and \textbf{keyword clustering} techniques to accurately retrieve products from the database based on complex user queries.}
        \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}