\documentclass[a4paper,11pt]{article}

% Packages
\usepackage[english]{babel}
\usepackage{latexsym}
\usepackage{marvosym}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{color}
\usepackage{hyperref}
\usepackage{verbatim}
\input{glyphtounicode}

% Page styling
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

% URL styling
\urlstyle{same}

% Set link color
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue
}

% Text alignment
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
}{}
{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumePosition}[4]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \small #4 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProject}[3]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \small#2 & \small\href{#1}{\underline{#3}} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Areeb Ahmed Shariff} \\ \vspace{1pt}
    \small (+91) 95913-07017 $|$ \href{mailto:areebshariff@acm.org}{\underline{areebshariff@acm.org}} $|$
    \href{https://linkedin.com/in/areebahmeddd}{\underline{linkedin.com/areebahmeddd}} $|$
    \href{https://github.com/areebahmeddd}{\underline{github.com/areebahmeddd}}
\end{center}

%----------EDUCATION----------
\section{Education}
\resumeSubHeadingListStart
    \resumePosition
        {Dayananda Sagar College of Engineering}{Bengaluru, India}
        {Bachelor of Engineering -- Computer Science and Business Systems}{2022 -- 2026}
    \resumePosition
        {Alpine Public School}{Bengaluru, India}
        {12th Standard}{2020 -- 2022}
\resumeSubHeadingListEnd

%----------TECHNICAL SKILLS----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=-2pt]
    \small{
        \item{\textbf{Frontend Development}{: JavaScript, HTML, CSS}}
        \item{\textbf{Developer Tools}{: MySQL, PostgreSQL, MongoDB, Amazon Web Services, Docker, Postman, GitHub}}
        \item{\textbf{Backend Development}{: Python, Java, Go, SQL}}
    }
\end{itemize}

%----------EXPERIENCE----------
\section{Experience}
\resumeSubHeadingListStart
    \resumePosition
        {Student Intern}{October 2023 -- November 2023}
        {National Institute of Technology Karnataka}{Bengaluru, India}
    \resumeItemListStart
        \resumeItem{Conducted API testing using Postman to validate HTTP responses and JSON data.}
        \resumeItem{Developed to-do web application using HTML, CSS, and JavaScript for task management and organization.}
        \resumeItem{Developed contact manager web application using MERN (MongoDB, Express.js, React, Node.js) stack, based on a client-server model for centralized contact storage.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%----------OPEN SOURCE CONTRIBUTION----------
\section{Open Source Contribution}
\resumeSubHeadingListStart
    \resumeProject
        {https://github.com/areebahmeddd/QuizQuest/commits?author=areebahmeddd}{\textbf{QuizQuest} $|$ \emph{TypeScript, Next.js, Tailwind, Firebase, Vercel}}{Contributions}
        \resumeItemListStart
            \resumeItem{Implemented \textbf{quiz lock and delete functionality} in admin panel.}
            \resumeItem{Improved admin panel UI by \textbf{enabling customizable quiz timer settings}.}
            \resumeItem{Fixed bugs related to \textbf{incorrect POST request to Firebase} and \textbf{inaccurate display of file name during quiz upload} in edge cases.}
        \resumeItemListEnd
\resumeSubHeadingListEnd

%----------PROJECTS----------
\section{Projects}
\resumeSubHeadingListStart
    \resumeProject
        {https://github.com/SpaceTesla/Mivro}{\textbf{Mivro} $|$ \emph{Django, OpenFoodFacts API, Gemini API, Firebase, AWS Amplify}}{GitHub}
        \resumeItemListStart
            \resumeItem{Developed cross-platform app and web extension for \textbf{personalized product profiling} across food, drinks, cosmetics, medicines, and pet food categories.}
            \resumeItem{Integrated \textbf{Gemini API} to \textbf{categorize nutrients based on user-specific health data} and \textbf{recommend healthier food options, supplements, or lifestyle changes}.}
            \resumeItem{Implemented custom searching algorithm using \textbf{fuzzy matching} and \textbf{keyword clustering} techniques to accurately retrieve products from the database based on complex user queries.}
        \resumeItemListEnd
    \resumeProject
        {https://github.com/areebahmeddd/GodsEye}{\textbf{GodsEye} $|$ \emph{FastAPI, BeautifulSoup, LangChain, Streamlit, MongoDB, Render Cloud}}{GitHub}
        \resumeItemListStart
            \resumeItem{Developed \textbf{automated feedback system} providing data visualizations on news article sentiment, organization-wise distribution, and overall coverage insights from selected news agencies.}
            \resumeItem{Implemented asynchronous processing using \textbf{Httpx library} to scrape articles from various media websites.}
            \resumeItem{Integrated \textbf{Gemini API} to identify trends such as trending topics, keywords, and analyze sentiment from the scraped article data.}
            \resumeItem{Designed UI using \textbf{Streamlit framework} and \textbf{Plotly library} to generate dynamic data visualizations using bar charts, pie charts, line charts, area charts, and more.}
        \resumeItemListEnd
    \resumeProject
        {https://github.com/areebahmeddd/Surf}{\textbf{Surf} $|$ \emph{Tkinter, BeautifulSoup, PyTesseract}}{GitHub}
        \resumeItemListStart
            \resumeItem{Developed \textbf{anonymous search engine} performing text and image searches across major engines--Google, Bing, and Yahoo.}
            \resumeItem{Implemented custom sorting algorithm using \textbf{Heap data structure} to rank top 10 out of 30 search results based on factors such as popularity and recency.}
            \resumeItem{Integrated proxy functionality using \textbf{PySocks library}, resulting in a 25\% drop in IP address tracking and a 15\% decrease in unauthorized attempts to access search result data.}
        \resumeItemListEnd
\resumeSubHeadingListEnd

%----------LEADERSHIP POSITION----------
\section{Leadership Position}
\resumeSubHeadingListStart
    \resumePosition
        {Founder}{September 2023 -- Present}
        {Scratch -- Dayananda Sagar Institutions}{Bengaluru, India}
    \resumeItemListStart
        \resumeItem{Organizing monthly Hackathons, Ideathons, and more.}
        \resumeItem{Conducting workshops on technologies such as Spatial Computing, 3D Printing, and more.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}